D.I.A.G.R.A.M.: Digital Image Analysis for Graph Recognition And Modeling

### 2025-07-09 doc/article/article.tex
UPDATE
Conclusion

\title{D.I.A.G.R.A.M.: Development of Image Analysis for Graph Recognition And Modeling}

@@

\section{Conclusion and Future Work}
TODO

>>>>

\title{D.I.A.G.R.A.M.: Digital Image Analysis for Graph Recognition And Modeling}

@@

\section{Conclusion and Future Work}
In this work, we introduced D.I.A.G.R.A.M., a system designed for the recognition and digitalization of visual diagrams. By combining deterministic algorithms with deep learning models, the system is capable of interpreting graphical input and converting it into structured, machine-readable formats. Our architecture demonstrates the feasibility of diagram understanding as a hybrid problem, leveraging both rule-based and learned components to achieve robustness and flexibility.

Despite the promising results, several opportunities remain for improvement. A key direction for future work is the parallelization of the extractor module, which currently represents a bottleneck in the processing pipeline. Efficient multi-threaded implementations could significantly speed up large-scale or real-time diagram analysis.

Additionally, to enhance portability and reproducibility, the system could benefit from containerization using Docker, particularly for managing CLI tools and Python dependencies. This would allow for more consistent deployment across diverse environments and simplify collaboration and maintenance.

Continued refinements in both the recognition pipeline and the system's usability will move us closer to a practical tool for academic, industrial, and educational use cases where diagram understanding and easy modeling is essential.
